\sysfull

### 2017-07-30 paper/systemdescription.tex

\begin{figure}
	\centering
	%\includegraphics[width=0.25\columnwidth]{figures/}
	\caption{\sys top-level description.}
	\label{fig:}
\end{figure}

Describe the overall system, the programming model, and the semantics/execution model. This should include a discussion of memory virtualization and task coalescing.

>>>>

\begin{figure}
	\centering
	%\includegraphics[width=0.25\columnwidth]{figures/}
	\caption{\sys top-level view.}
	\label{fig:system_overview}
\end{figure}

\sys as a whole is characterized by the following features:

\begin{itemize}
	\item \textbf{Task coalescing}: details will be provided in Section~\ref{sec:task_coalescing}
	\item \textbf{Memory virtualization}: details will be provided in Section~\ref{sec:memory_virtulaization}
	\item \textbf{Compiler support}: details will be provided in Section~\ref{sec:compiler}
\end{itemize}

A complete logical structure of \sys is given in Figure~\ref{fig:system_overview}. Before describing each feature of \sys in detail we need to introduce a programming and semantics/execution model.

\subsection{Programming Model}
\label{sec:overview_programming_model}

\subsection{Semantics and Execution Model}
\label{sec:overview_semantics}
